Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-22 paper/paper.Rmd
fix bug caused by changes to metadata code

# Models coverage of forecast dates
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```

>>>>

# Models coverage of forecast dates
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "forecast_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```
